Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-05-24 Multiresolution_framework/ltx/manuscript.tex
updated Mike affiliation
added discussion about isotropy for switching the inner product and convolution

\author[TNG]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE]{D. R. Freestone}
\ead{deanrf@unimelb.edu.au} 
\author[CU]{M. Dewar}
\ead{mike.dewar@columbia.edu}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt} 
 \author[TNG]{V. Jirsa}
\ead{viktor.jirsa@univ-amu.fr}
\author[DEEE]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

\address[TNG]{Theoretical Neuroscience Group, UMR 1106, Institut de Neurosciences des Systemes, 13385 Marseille, France}
\address[DEEE]{NeuroEngineering Laboratory, Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
\address[CU]{Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
 \address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}

@@

>>>>

\author[TNG]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE]{D. R. Freestone}
\ead{deanrf@unimelb.edu.au} 
\author[CU]{M. Dewar}
\ead{md@bit.ly}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt} 
 \author[TNG]{V. Jirsa}
\ead{viktor.jirsa@univ-amu.fr}
\author[DEEE]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

\address[TNG]{Theoretical Neuroscience Group, UMR 1106, Institut de Neurosciences des Systemes, 13385 Marseille, France}
\address[DEEE]{NeuroEngineering Laboratory, Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, VIC, Australia}
\address[CU]{bit.ly, New York City, USA}
\address[UM]{Department of Systems and Control Engineering, University of Malta, Msida, MSD, Malta}
 \address[US]{Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, UK}

@@

Choosing isotropic scaling and wavelet functions allows switching the order of operations with the inner product and convolution in Eq.~\eqref{eq:ApproxDiscreteTimeModel4}. This simplifies the computational complexity of the estimation algorithm significantly. Although this is correct for one dimensional B-spline scaling and wavelet functions, it does not hold at higher dimensions as the resulting B-spline wavelets are not isotropic. One alternative could be  
isotropic polyharmonic B-splines scaling functions and wavelets \citep{VanDeVille2005}.
